### 2024-10-10 paper/paper.qmd
Code Added to the Paper

```{r}
#| include: false
#| warning: false
#| message: false
radiohead  <- readRDS(here("spotify_api/data/00-raw_data/radiohead.rds"))
radiohead
```

```{r}
#| warning: false
#| message: false
#| echo:    false
radiohead <- as_tibble(radiohead)

radiohead |>
  mutate(album_release_date = ymd(album_release_date)) |>
  ggplot(aes(
    x = album_release_date,
    y = duration_ms,
    group = album_release_date
  )) +
  geom_boxplot() +
  geom_jitter(alpha = 0.5, width = 0.3, height = 0) +
  theme_minimal() +
  labs(
    x = "Album release date",
    y = "Duration of song (ms)"
  )
```

```{r}
#| warning: false
#| message: false
#| echo:    false
rbind( the_national, radiohead) |>
  select(artist_name, album_release_date, valence) |>
  mutate(album_release_date = ymd(album_release_date)) |> 
  ggplot(aes( x = album_release_date, y = valence, color = artist_name)) +
  geom_point(alpha = 0.3) +
  geom_smooth() +
  theme_minimal() +
  facet_wrap(facets = vars(artist_name), dir = "v") +
  labs(
    x = "Album release date",
    y = "Valence",
    color = "Artist"
  ) +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom")
```

>>>>

```{r}
#| include: false
#| warning: false
#| message: false
the_chainsmokers <- readRDS(here("data/00-raw_data/the_chainsmokers.rds"))
the_chainsmokers
```

```{r}
#| warning: false
#| message: false
#| echo:    false
the_chainsmokers |>
  mutate(album_release_date = ymd(album_release_date)) |>
  ggplot(aes(
    x = album_release_date,
    y = duration_ms,
    group = album_release_date
  )) +
  geom_boxplot() +
  geom_jitter(alpha = 0.5, width = 0.3, height = 0) +
  theme_minimal() +
  labs(
    x = "Album release date",
    y = "Duration of song (ms)"
  )
```

```{r}
#| warning: false
#| message: false
#| echo:    false
#| fig-align: "center"
#| fig-width: 10
#| fig-height: 6
audio_features <- c('danceability', 'energy', 'speechiness', 'acousticness', 
                    'instrumentalness', 'liveness', 'valence')
the_chainsmokers_filtered <- the_chainsmokers %>%
  filter(album_name != "So Far So Good (lofi remixes)")

album_comparison <- the_chainsmokers_filtered %>%
  group_by(album_name) %>%
  summarise(across(all_of(audio_features), mean, na.rm = TRUE))

album_comparison_long <- tidyr::pivot_longer(album_comparison, 
                                             cols = audio_features, 
                                             names_to = "feature", 
                                             values_to = "mean_value")
ggplot(album_comparison_long, aes(x = album_name, y = mean_value, fill = feature)) +
  geom_bar(stat = "identity", position = "dodge") +
  labs(x = "Album Name", y = "Mean Value", 
       title = "Comparison of Audio Features by Album (Excluding Loudness and Tempo)") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1, size = 8, margin = margin(t = 10))) + 
  theme_minimal()
```
